The Effects of Labor-Associated Drug Interventions on Neonatal Health Outcomes: A Predictive Analysis of Apgar5 Scores

### 2024-12-03 paper/paper.qmd
fix citation errors

## Model set-up

@@

### Model Specification

#### Random Forest Model

@@

#### Bayesian Linear Model

@@

### Model justification

@@

```{r}
#| label: fig-result1
#| fig-cap: The mean of Apgar5 scores by the number of treatments received during labor and delivery (**Note:** The dark blue lines represent error bars, indicating the variability or uncertainty around the mean Apgar5 scores for each number of treatments.)
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-indcscore
#| fig-cap: Apgar5 score distribution for the usage of induction labor (**Note:** The red line represents a visual summary of how observation counts change along the score range.)
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-augmtscore
#| fig-cap: Apgar5 score distribution for the usage of augmentation labor (**Note:** The red line represents a visual summary of how observation counts change along the score range.)
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-sterscore
#| fig-cap: Apgar5 score distribution for the usage of steroids (**Note:** The red line represents a visual summary of how observation counts change along the score range.)
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-antbscore
#| fig-cap: Apgar5 score distribution for the usage of antibiotics (**Note:** The red line represents a visual summary of how observation counts change along the score range.)
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-chorscore
#| fig-cap: Apgar5 score distribution for the usage of chorioamnionitis (**Note:** The red line represents a visual summary of how observation counts change along the score range.)
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-anesscore
#| fig-cap: Apgar5 score distribution for the usage of anesthesia (**Note:** The red line represents a visual summary of how observation counts change along the score range.)
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| echo: false
#| eval: true
#| label: fig-rfsumbar
#| fig-cap: Variable importance of treatments during labor and delivery on infant health, expressed in bar plots
#| warning: false

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: Bayesian linear models quantifying the effects of medical interventions during labor and delivery on infant health outcomes
#| warning: false

>>>>

## Model Specification

@@

### Random Forest Model

@@

### Bayesian Linear Model

@@

## Model Justification

@@

```{r}
#| label: fig-result1
#| fig-cap: Average Apgar5 scores by the number of treatments received during labor and delivery (**Note:** The dark blue lines represent error bars, indicating the variability or uncertainty around the mean Apgar5 scores for each number of treatments.)
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-indcscore
#| fig-cap: Apgar5 score distribution for infants who received induction of labor
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-augmtscore
#| fig-cap: Apgar5 score distribution for infants who received augmentation of labor
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-sterscore
#| fig-cap: Apgar5 score distribution for infants who received steroids dosage
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-antbscore
#| fig-cap: Apgar5 score distribution for infants who received antibiotics dosage
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-chorscore
#| fig-cap: Apgar5 score distribution for infants who received chorioamnionitis dosage
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-anesscore
#| fig-cap: Apgar5 score distribution for infants who received anesthesia dosage
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| echo: false
#| eval: true
#| label: fig-rfsumbar
#| fig-cap: Horizontal bar plot showing the variable importance of treatments during labor and delivery on infant health
#| warning: false

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: Summary of a bayesian linear model quantifying the effects of medical interventions during labor and delivery on infant health outcomes
#| warning: false
